### 2021-04-28 evaluation.tex
Revert "consistent cref"
This reverts commit 4a035ede5ffc8e31b4d41461b8d1a5eee540508e.
Avoid an overfull line in non-compressed version

To generate a precedence for a problem,
\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit of 10 seconds was only imposed on the \Vampire{} run,
excluding the time taken by the recommender to generate the precedence.
When run with 2 threads,
the preprocessing of a single problem
took at most \num[round-mode=places,round-precision=2]{1.263048204} seconds
for \SI{80}{\percent} of the problems
by extrapolation from a sample of \num{1000} problems.\footnote{The remaining \SI{20}{\percent} of the problems either finished preprocessing within 5 seconds, or were omitted from preprocessing due to exceeding the node count limit.}
% \num[round-mode=places,round-precision=2]{4.745481158}
\todo[author=FB]{Is the footnote with maximum observed time worth the space?}
% Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
% VML-715
\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
\cref{tab:results} shows the results of the final evaluation.

@@

We confirmed our earlier conjecture \cite{DBLP:conf/cade/Bartek020} that using a \gls{gnn}
may outperform the ``simple'' linear predicate precedence heuristic
trained in \cite{DBLP:conf/cade/Bartek020}.\footnote{The measurements presented in \cref{tab:results}
are not directly comparable with those reported in \cite{DBLP:conf/cade/Bartek020}
due to differences in the validation problem sets and the computation environments.}

>>>>

To generate a precedence for a problem,
\todo{MS: tenhle odstavec mozna prehodit s predchozim?}
the recommender first converts the problem to a machine-friendly \gls{cnf} format,
then converts the \gls{cnf} to a graph,
then predicts symbol costs using the \gls{gcn} model
and finally orders the symbols by their costs to produce the precedence.
To simplify the experiment, the time limit of 10 seconds was only imposed on the \Vampire{} run,
excluding the time taken by the recommender to generate the precedence.
When run with 2 threads,
the preprocessing of a single problem
took at most \num[round-mode=places,round-precision=2]{1.263048204} seconds
for \SI{80}{\percent} of the problems
by extrapolation from a sample of \num{1000} problems.\footnote{The remaining \SI{20}{\percent} of the problems either finished preprocessing within 5 seconds, or were omitted from preprocessing due to exceeding the node count limit.}
% \num[round-mode=places,round-precision=2]{4.745481158}
\todo[author=FB]{Is the footnote with maximum observed time worth the space?}
% Analysis: https://docs.google.com/spreadsheets/d/1GujYNEtETpC3jk4iyENLjptv8mDmI5f1ZEhbmwtqnPM/edit?usp=sharing
% VML-715
\todo{MS: 1) single-core bych chapal jako default. tj netreba zminovat?
2) kterych 1000? To opet drazdi k otazkam. tj to bych asi taky vynechal, ale...
3) to maximum prece zalezi na tom, kterych 1000 to bylo.}
\todo{MS: Idea: kdyz je to linearni: co cas potrebny na recommending
vztahnout k casu klauzifikace? Jako rict, ze to trva x-krat dyl nez jen klauzifikovat?}
\Cref{tab:results} shows the results of the final evaluation.

@@

We have confirmed our earlier conjecture \cite{DBLP:conf/cade/Bartek020} that using a \gls{gnn}
may outperform the ``simple'' linear predicate precedence heuristic
trained in \cite{DBLP:conf/cade/Bartek020}.\footnote{The measurements presented in \cref{tab:results}
are not directly comparable with those reported in \cite{DBLP:conf/cade/Bartek020}
due to differences in the validation problem sets and the computation environments.}
